---
title: "COVID-19 Mental Health Search Terms"
author: "Bruno Salgado"
output: pdf_document
---

```{r include=FALSE}
# Load library and data
library(ggplot2)
library(plyr)
library(readxl)
library(wesanderson)
require(maps)
data_us <- read_excel("search_term_us.xlsx")
data_ca <- read_excel("search_term_canada.xlsx")
data_uk <- read_excel("search_term_uk.xlsx")

df_us <- data.frame(data_us)
df_ca <- data.frame(data_ca)
df_uk <- data.frame(data_uk)

knitr::opts_chunk$set(echo = T, results = "hide")
```

## Mental Health Search Terms

The following graphs show the frequency of search terms related to mental 
health topics before and during the COVID-19 pandemic.

The data is produced from Google's search term frequency tool and the populations 
observed are from the U.S., Canada, and the U.K..

### Depression

#### U.S.
```{r, message=FALSE}
us <- ggplot(df_us, aes(x = Week, y = depression)) +
  geom_point(color=wes_palettes$FantasticFox1[5]) +
  geom_smooth(method = lm, color = wes_palettes$FantasticFox1[4],
              fill=wes_palettes$FantasticFox1[3]) +
  labs(title = "U.S. Depression Search Interest")

us
```

#### Canada
```{r, message=FALSE}
ca <- ggplot(df_ca, aes(x = Week, y = depression)) +
  geom_point(color=wes_palettes$FantasticFox1[5]) +
  geom_smooth(method = lm, color = wes_palettes$FantasticFox1[4],
              fill=wes_palettes$FantasticFox1[3]) +
  labs(title = "Canada Depression Search Interest")

ca
```

#### U.K.
```{r, message=FALSE}
uk <- ggplot(df_uk, aes(x = Week, y = depression)) +
  geom_point(color=wes_palettes$FantasticFox1[5]) +
  geom_smooth(method = lm, color = wes_palettes$FantasticFox1[4],
              fill=wes_palettes$FantasticFox1[3]) +
  labs(title = "U.K. Depression Search Interest")

uk
```

### Anxiety and Psychiatry

The following graphs will show the relationship between "anxiety" and "psychiatry" 
and how often these two search terms appear together with respect to time during 
the pandemic.

#### U.S.
```{r, message=FALSE}
us_psy <- ggplot(df_us, aes(x = Week, y = anxiety, fill = psychiatrist)) +
  geom_tile() +
  scale_fill_gradientn(colors = wes_palette("FantasticFox1", type="continuous")) +
  labs(title = "U.S. Anxiety and Psychiatrist Search Interest")

us_psy
```

#### Canada
```{r, message=FALSE}
ca_psy <- ggplot(df_ca, aes(x = Week, y = anxiety, fill = psychiatrist)) +
  geom_tile() +
  scale_fill_gradientn(colors = wes_palette("FantasticFox1", type="continuous")) +
  labs(title = "Canada Anxiety and Psychiatrist Search Interest")

ca_psy
```

#### U.K.
```{r, message=FALSE}
uk_psy <- ggplot(df_uk, aes(x = Week, y = anxiety, fill = psychiatrist)) +
  geom_tile() +
  scale_fill_gradientn(colors = wes_palette("FantasticFox1", type="continuous")) +
  labs(title = "U.K. Anxiety and Psychiatrist Search Interest")

uk_psy
```