---
title: "Stack Overflow Tag Network"
author: "Bruno Salgado"
date: "1/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 15, fig.height = 10)
library(ggplot2)
library(readr)
library(igraph)
library(ggraph)
library(tidyverse)
library(wesanderson)

nodes <- read.csv("./stack_network_nodes.csv")
edges <- read.csv("./stack_network_links.csv")

graph <- graph_from_data_frame(d = edges, vertices = nodes, directed = FALSE)

pal <- wes_palette("IsleofDogs1")
```

## Introduction

Stack Overflow is an online forum centered around users asking and answering each
others' questions surrounding different topics in the software engineering field.

Users can add tags to their question to highlight the main programming language
or technology that their question is about. For example, if a user asked a
question about using databases in C++, they might include tags such as "databases"
and "c++."

This report aims to demonstrate how tags on the website are related to each other
and visualize all the different connections the topics have when questions are
asked about them.

# Network Topology

To get a general idea of how the Stack Overflow tags are related to each other,
this figure presents the entire unadulterated network topology. Notice the
independent clusters that form outside of the main group.

```{r}
ggraph(graph, layout = 'stress') +
  geom_edge_link(aes(colour = factor(value)), show.legend = FALSE) +
  geom_node_point() +
  theme_graph(background = pal[4], text_colour = pal[5])
```

# Chord Diagram

This chord diagram shows the relationship between topics and specifically how
each topic flows from one to another.

```{r}
V(graph)$id=NA
myleaves=which(is.na( match(V(graph)$name, E(graph)$from) ))
nleaves=length(myleaves)
V(graph)$id[ myleaves ] = seq(1:nleaves)
V(graph)$angle= 90 - 360 * V(graph)$id / nleaves
V(graph)$angle<-ifelse(V(graph)$angle < -90, V(graph)$angle+180, V(graph)$angle)

ggraph(graph, layout = "linear", circular = TRUE) +
  geom_edge_arc(aes(width = value, edge_colour = factor(value)), show.legend = FALSE, alpha = 0.5) +
  geom_node_point(aes(color = factor(group), size = nodesize * 51)) +
  geom_node_text(aes(label = name, angle = V(graph)$angle), hjust = "outward", size = 4, color = pal[5]) + 
  theme_graph(background = pal[4], text_colour = pal[5]) +
  expand_limits(x = c(-1.2, 1.2))
```

# Arc Diagram

Finally, this arc diagram illustrates the connection between the tags on a
one-dimensional axis.

```{r}
ggraph(graph, layout = "linear") +
  geom_edge_arc(aes(width = value, edge_colour = factor(value)), show.legend = FALSE, alpha = 0.5, fold = FALSE) +
  geom_node_point(aes(color = factor(group))) +
  geom_node_text(aes(label = name, angle = 90, hjust = "right"), nudge_y = -0.5, color = pal[5], size = 4) +
  theme_graph(background = pal[4], text_colour = pal[5]) +
  theme(legend.position = "none") +
  expand_limits(x = c(-1.2, 1.2), y = c(-5.6, 1.2))
```

```{css}
body {
  background-color: #000;
  color: #D9D0D3;
}

h1 {
  color: #CCBA72;
}

h2 {
  color: #8D8680;
}

body .main-container {
  max-width: 80vw;
}
```
